Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-06 SupportingInformation.Rmd
code changed

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

  # for clayton with spearman and kendall method
    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

@@

  # for survival clayton with spearman and kendall method
    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

@@

  # for gumbel with spearman and kendall method
    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

@@

  # for survival gumbel with spearman and kendall method
    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

@@

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

@@

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```
<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}
--->

>>>>

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
ar1_C_spear_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

saveRDS(ar1_C_spear_beta0.5,paste(resloc,"ar1_C_spear_beta0.5.RDS",sep=""))

ar1_C_kend_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=c(0,0),model=model)

saveRDS(ar1_C_kend_beta0.5,paste(resloc,"ar1_C_kend_beta0.5.RDS",sep=""))

@@

resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
ar1_C_spear_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                              num_keep_last=500,resloc=resloc,
                                              params=params,p0=c(0,0),model=model)

saveRDS(ar1_C_spear_negbeta0.5,paste(resloc,"ar1_C_spear_negbeta0.5.RDS",sep=""))

ar1_C_kend_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                               num_keep_last=500,resloc=resloc,
                                               params=params,p0=c(0,0),model=model)

saveRDS(ar1_C_kend_negbeta0.5,paste(resloc,"ar1_C_kend_negbeta0.5.RDS",sep=""))
```

```{r plot_cause4copula_stat_ar1_clayton, echo=F, results="hide", cache=T, cache.extra=list(seed,ar1_C_spear_beta0.5,ar1_C_spear_negbeta0.5,ar1_C_kend_beta0.5,ar1_C_kend_negbeta0.5,mtime("Plotter_Cause4copula_stat.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ar1"
fcode<-3
resloc0<-"./Results/Cause4copula_results/"

tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_C_spear_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
readres<-readRDS(paste(resloc,"ar1_C_kend_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)

# for negative beta
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_C_spear_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
readres<-readRDS(paste(resloc,"ar1_C_kend_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
```

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
ar1_SC_spear_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                            num_keep_last=500,resloc=resloc,
                                            params=params,p0=c(0,0),model=model)

saveRDS(ar1_SC_spear_beta0.5,paste(resloc,"ar1_SC_spear_beta0.5.RDS",sep=""))

ar1_SC_kend_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

saveRDS(ar1_SC_kend_beta0.5,paste(resloc,"ar1_SC_kend_beta0.5.RDS",sep=""))
# for negative beta
params<-c(-0.5) # this parameter is beta in ar1 model

@@

resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
ar1_SC_spear_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                               num_keep_last=500,resloc=resloc,
                                               params=params,p0=c(0,0),model=model)
saveRDS(ar1_SC_spear_negbeta0.5,paste(resloc,"ar1_SC_spear_negbeta0.5.RDS",sep=""))

ar1_SC_kend_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                              num_keep_last=500,resloc=resloc,
                                              params=params,p0=c(0,0),model=model)
saveRDS(ar1_SC_kend_negbeta0.5,paste(resloc,"ar1_SC_kend_negbeta0.5.RDS",sep=""))
```

```{r plot_cause4copula_stat_ar1_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,ar1_SC_spear_beta0.5,ar1_SC_spear_negbeta0.5,ar1_SC_kend_beta0.5,ar1_SC_kend_negbeta0.5,mtime("Plotter_Cause4copula_stat.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ar1"
fcode<-13
resloc0<-"./Results/Cause4copula_results/"

tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_SC_spear_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
readres<-readRDS(paste(resloc,"ar1_SC_kend_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)

# for negative beta
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_SC_spear_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
readres<-readRDS(paste(resloc,"ar1_SC_kend_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
```

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for gumbel with spearman and kendall method
ar1_G_spear_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                              num_keep_last=500,resloc=resloc,
                                              params=params,p0=c(0,0),model=model)
saveRDS(ar1_G_spear_beta0.5,paste(resloc,"ar1_G_spear_beta0.5.RDS",sep=""))

ar1_G_kend_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                             num_keep_last=500,resloc=resloc,
                                             params=params,p0=c(0,0),model=model)

saveRDS(ar1_G_kend_beta0.5,paste(resloc,"ar1_G_kend_beta0.5.RDS",sep=""))

@@

resloc<-paste(tempo,"/",sep="")
# for gumbel with spearman and kendall method
ar1_G_spear_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                              num_keep_last=500,resloc=resloc,
                                              params=params,p0=c(0,0),model=model)
saveRDS(ar1_G_spear_negbeta0.5,paste(resloc,"ar1_G_spear_negbeta0.5.RDS",sep=""))

ar1_G_kend_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                             num_keep_last=500,resloc=resloc,
                                             params=params,p0=c(0,0),model=model)

saveRDS(ar1_G_kend_negbeta0.5,paste(resloc,"ar1_G_kend_negbeta0.5.RDS",sep=""))
```

```{r plot_cause4copula_stat_ar1_gumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,ar1_G_spear_beta0.5,ar1_G_spear_negbeta0.5,ar1_G_kend_beta0.5,ar1_G_kend_negbeta0.5,mtime("Plotter_Cause4copula_stat.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ar1"
fcode<-4
resloc0<-"./Results/Cause4copula_results/"

tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_G_spear_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
readres<-readRDS(paste(resloc,"ar1_G_kend_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)

# for negative beta
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_G_spear_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
readres<-readRDS(paste(resloc,"ar1_G_kend_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
```

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival gumbel with spearman and kendall method
ar1_SG_spear_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                              num_keep_last=500,resloc=resloc,
                                              params=params,p0=c(0,0),model=model)
saveRDS(ar1_SG_spear_beta0.5,paste(resloc,"ar1_SG_spear_beta0.5.RDS",sep=""))

ar1_SG_kend_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                             num_keep_last=500,resloc=resloc,
                                             params=params,p0=c(0,0),model=model)

saveRDS(ar1_SG_kend_beta0.5,paste(resloc,"ar1_SG_kend_beta0.5.RDS",sep=""))

@@

resloc<-paste(tempo,"/",sep="")
# for survival gumbel with spearman and kendall method
ar1_SG_spear_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                              num_keep_last=500,resloc=resloc,
                                              params=params,p0=c(0,0),model=model)
saveRDS(ar1_SG_spear_negbeta0.5,paste(resloc,"ar1_SG_spear_negbeta0.5.RDS",sep=""))

ar1_SG_kend_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                             num_keep_last=500,resloc=resloc,
                                             params=params,p0=c(0,0),model=model)

saveRDS(ar1_SG_kend_negbeta0.5,paste(resloc,"ar1_SG_kend_negbeta0.5.RDS",sep=""))
```

```{r plot_cause4copula_stat_ar1_survivalgumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,ar1_SG_spear_beta0.5,ar1_SG_spear_negbeta0.5,ar1_SG_kend_beta0.5,ar1_SG_kend_negbeta0.5,mtime("Plotter_Cause4copula_stat.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ar1"
fcode<-14
resloc0<-"./Results/Cause4copula_results/"

tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_SG_spear_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
readres<-readRDS(paste(resloc,"ar1_SG_kend_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)

# for negative beta
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_SG_spear_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
readres<-readRDS(paste(resloc,"ar1_SG_kend_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
```

@@

ar1_J_kend_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                             num_keep_last=500,resloc=resloc,
                                             params=params,p0=c(0,0),model=model)

saveRDS(ar1_J_kend_beta0.5,paste(resloc,"ar1_J_kend_beta0.5.RDS",sep=""))

@@

ar1_J_kend_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                             num_keep_last=500,resloc=resloc,
                                             params=params,p0=c(0,0),model=model)

saveRDS(ar1_J_kend_negbeta0.5,paste(resloc,"ar1_J_kend_negbeta0.5.RDS",sep=""))
```

```{r plot_cause4copula_stat_ar1_joe, echo=F, results="hide", cache=T, cache.extra=list(seed,ar1_J_kend_beta0.5,ar1_J_kend_negbeta0.5,mtime("Plotter_Cause4copula_stat.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ar1"
fcode<-6
resloc0<-"./Results/Cause4copula_results/"

tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_J_kend_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)

# for negative beta
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_J_kend_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
```

@@

ar1_SJ_kend_beta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                             num_keep_last=500,resloc=resloc,
                                             params=params,p0=c(0,0),model=model)

saveRDS(ar1_SJ_kend_beta0.5,paste(resloc,"ar1_SJ_kend_beta0.5.RDS",sep=""))

@@

ar1_SJ_kend_negbeta0.5<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                             num_keep_last=500,resloc=resloc,
                                             params=params,p0=c(0,0),model=model)

saveRDS(ar1_SJ_kend_negbeta0.5,paste(resloc,"ar1_SJ_kend_negbeta0.5.RDS",sep=""))
```

```{r plot_cause4copula_stat_ar1_survivaljoe, echo=F, results="hide", cache=T, cache.extra=list(seed,ar1_SJ_kend_beta0.5,ar1_SJ_kend_negbeta0.5,mtime("Plotter_Cause4copula_stat.R"))}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ar1"
fcode<-16
resloc0<-"./Results/Cause4copula_results/"

tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_SJ_kend_beta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)

# for negative beta
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc0,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")
resloc<-paste(tempo,"/",sep="")

readres<-readRDS(paste(resloc,"ar1_SJ_kend_negbeta0.5.RDS",sep=""))
Plotter_Cause4copula_stat(res=readres)
```

@@

  # for clayton with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_C_spear.RDS",sep=""))

    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_C_kend.RDS",sep=""))

  }
 }
}
```

```{r plot_cause4copula_stat_ricker_C, echo=F, results="hide"}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ricker"
fcode<-3
resloc0<-"./Results/Cause4copula_results/"

    resloc<-paste(tempo,"/",sep="")

    readres<-readRDS(paste(resloc,"ricker_C_spear.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)
    readres<-readRDS(paste(resloc,"ricker_C_kend.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)

  }
 }
}
```

@@

  # for survival clayton with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_SC_spear.RDS",sep=""))

    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_SC_kend.RDS",sep=""))
  }
 }
}
```

```{r plot_cause4copula_stat_ricker_SC, echo=F, results="hide"}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ricker"
fcode<-13
resloc0<-"./Results/Cause4copula_results/"

    resloc<-paste(tempo,"/",sep="")

    readres<-readRDS(paste(resloc,"ricker_SC_spear.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)
    readres<-readRDS(paste(resloc,"ricker_SC_kend.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)

  }
 }
}
```

@@

  # for gumbel with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_G_spear.RDS",sep=""))

    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_G_kend.RDS",sep=""))
  }
 }
}
```

```{r plot_cause4copula_stat_ricker_G, echo=F, results="hide"}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ricker"
fcode<-4
resloc0<-"./Results/Cause4copula_results/"

    resloc<-paste(tempo,"/",sep="")

    readres<-readRDS(paste(resloc,"ricker_G_spear.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)
    readres<-readRDS(paste(resloc,"ricker_G_kend.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)

  }
 }
}
```

@@

  # for survival gumbel with spearman and kendall method
    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,
                                           num_keep_last=500,resloc=resloc,
                                           params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_SG_spear.RDS",sep=""))

    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_SG_kend.RDS",sep=""))
  }
 }
}
```

```{r plot_cause4copula_stat_ricker_SG, echo=F, results="hide"}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ricker"
fcode<-14
resloc0<-"./Results/Cause4copula_results/"

    resloc<-paste(tempo,"/",sep="")

    readres<-readRDS(paste(resloc,"ricker_SG_spear.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)
    readres<-readRDS(paste(resloc,"ricker_SG_kend.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)

  }
 }
}
```

@@

    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_J_kend.RDS",sep=""))
  }
 }
}
```

```{r plot_cause4copula_stat_ricker_J, echo=F, results="hide"}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ricker"
fcode<-6
resloc0<-"./Results/Cause4copula_results/"

    resloc<-paste(tempo,"/",sep="")

    readres<-readRDS(paste(resloc,"ricker_J_kend.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)

  }
 }
}
```

@@

    myres<-Sim_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,
                                          num_keep_last=500,resloc=resloc,
                                          params=params,p0=c(0,0),model=model)

    saveRDS(myres,paste(resloc,"ricker_J_kend.RDS",sep=""))
  }
 }
}
```

```{r plot_cause4copula_stat_ricker_SJ, echo=F, results="hide"}

set.seed(seed)
source("Plotter_Cause4copula_stat.R")
#---------------------------------------
# This chunk plots results for ar1 model : clayton

model<-"ricker"
fcode<-16
resloc0<-"./Results/Cause4copula_results/"

    resloc<-paste(tempo,"/",sep="")

    readres<-readRDS(paste(resloc,"ricker_SJ_kend.RDS",sep=""))
    Plotter_Cause4copula_stat(res=readres)

  }
 }
}
```
<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}
--->
